%!TEX program = lualatex
%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Jacob Meyers}
\address{2319 Franklin Ave E \# B \linebreak Seattle, WA 98102}
\contacts{(229) 506-1157 \linebreak jacobmeyers065@gmail.com}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	
	\begin{cvsection}{Experience}
	
		\begin{cvsubsection}{Software Engineer}{Microsoft}{July 2020 -- Present}
			\emph{Microsoft Teams Calling, Meetings, and Devices}
			\begin{itemize}
				\item Working on calling and meetings features for the Microsoft Teams web client.
				\item Implemented and shipped client-side code for screensharing presenter modes in collaboration with two teammates, which sees around 100,000 uses per day.
				\item Designed and drove client-side implementation for key features for Teams VDI solution, including multi-window experience, background effects, and give/take control during screensharing. Many of these features are top customer blockers for migration from Skype for Business. Defined E2E designs in collaboration with internal and external partners.
				\item Designed, implemented, and supported various background effects features, including branded backgrounds, background blur for anonymous users, and separate backgrounds for consumer Teams.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Engineering Intern}{Visa, Inc}{May 2019 -- August 2019}
		\emph{Merchant and Acquirer Processing Site Reliability Engineering	}
			\begin{itemize}
				\item Designed and implemented RESTful service to serve as single point of integration for thousands of monitoring alerts from several different tools to display in a unified UI.
				\item Integrated Grafana into alert service as a UI and built dashboards to display previously unavailable aggregations and visualizations of alert data.			
			\end{itemize}
		\end{cvsubsection}
						
				\begin{cvsubsection}{Software Engineering Intern}{Datamaxx Group}{May 2018 -- August 2018}		
		\emph{Redtail Security}
			\begin{itemize}
				\item Implemented drug screening features for enterprise security and screening web application used by several collegiate and professional sports teams and the United States Army Corps of Engineers.
				\item Contributed code now in production across the entire stack, from UI components using HTML, jQuery, and Bootstrap to backend APIs in C\#.
				\item Assisted in QA efforts and found and fixed several previously unknown issues before release to production.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Teaching Assistant}{Georgia Institute of Technology}{August 2017 -- May 2020}
			\begin{itemize}
				\item Courses: Intro to Object Oriented Programming, Systems and Networks (Head Teaching Assistant)
				\item Hired, managed, and mentored a team of 12 teaching assistants.
				\item Created and presented course material to students in weekly recitations and held office hours to help students debug assignments such as a virtual memory simulator and multi-threaded networking project.
				\item Developed new course materials and developed infrastructure on the fly to facilitate the sudden shift to distance learning for 250 students in response to COVID-19.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
		\begin{cvsection}{Education}
		\begin{cvsubsection}{Atlanta, GA}{Georgia Institute of Technology}{Fall 2016 -- May 2020}
			\begin{itemize}
				\item Awarded Bachelor's of Science in Computer Science
				\item GPA: 3.70 / 4.0
				\item Concentrations: Systems and Architecture, Artificial Intelligence
				\item Accolades: Outstanding Undergraduate Teaching Assistant (2020), Dean's List (all semesters), Faculty Honors (Spring 2019, Spring 2020)
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item Javascript/Typescript, Java, Python, C, C\#
				\item React, GraphQL, Angular
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}
